Results

### 2018-09-21 4-results-simus.Rmd
polish SupMat
begin renaming

```{r}
library(tidyverse)
# devtools::install_github("privefl/bigsnpr")
library(bigsnpr)
# devtools::install_github("privefl/paper2-PRS/pkg.paper.PRS")
library(pkg.paper.PRS)  ## See code source for functions' code.
options(nboot = 1e4)
```

@@

```{r, message=FALSE}
COLORS <- scales::hue_pal()(6)
methods.color <- setNames(
  c(COLORS, COLORS[c(4, 2, 5)], "black"), 
  c("logit-simple", "PRS-max", "PRS-stringent", "T-Trees", "logit-triple", "PRS-all",
    "PRS-max-0.05", "PRS-max-0.2", "PRS-max-0.8", "biglasso")
) 
```

>>>>

```{r}
library(tidyverse)
# devtools::install_github("privefl/bigsnpr")
library(bigsnpr)
# devtools::install_github("privefl/paper2-PRS/pkg.paper.PRS")
library(pkg.paper.PRS)  ## See code source for functions' code.
options(nboot = 1e3)
```

@@

```{r, message=FALSE}
COLORS <- scales::hue_pal()(6)
methods.color <- setNames(
  c(COLORS, COLORS[c(4, 2, 5)], "black"), 
  c("PLR", "C+T-max", "C+T-stringent", "T-Trees", "PLR3", "C+T-all",
    "C+T-max-0.05", "C+T-max-0.2", "C+T-max-0.8", "biglasso")
) 
```
